---
title: "STAT/MATH 495: Problem Set 07"
author: "Caleb Brooks"
date: "2017-10-24"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 2
    collapsed: false
    smooth_scroll: false
    df_print: kable
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE, fig.width=8, fig.height=4.5, message=FALSE, warning = FALSE
  )
set.seed(76)

# Load packages
library(tidyverse)
library(broom)
library(knitr)
library(ROCR)
library(caret)
library(MLmetrics)

train <- read_csv("data/cs-training.csv") %>% 
  rename(Id = X1)
test <- read_csv("data/cs-test.csv") %>% 
  rename(Id = X1)
submission <- read_csv("data/sampleEntry.csv")
```

Information on the competition can be found [here](https://www.kaggle.com/c/GiveMeSomeCredit/data).



# Collaboration

Please indicate who you collaborated with on this assignment: 



# Build binary classifier

Build the binary classifier based on a single predictor variable: `DebtRatio`,
`age`, or `MonthlyIncome`. Justify this choice.

```{r}
boxplot(log(train$DebtRatio)~train$SeriousDlqin2yrs, ylab = "log(Debt Ratio)", xlab = "Serious delinquency (0 = no, 1 = yes)", title = "Debt ratio by occurance of delinquency")
boxplot(train$age~train$SeriousDlqin2yrs, ylab = "Age", xlab = "Serious delinquency (0 = no, 1 = yes)", title = "Age by occurance of delinquency")
boxplot(log(train$MonthlyIncome)~train$SeriousDlqin2yrs, ylab = "log(Monthly income)", xlab = "Serious delinquency (0 = no, 1 = yes)", title = "Monthly income by occurance of delinquency")
#Age seems to present the clearest difference between the behavior of the response variable

model_formula <- as.formula(train$SeriousDlqin2yrs~train$age)
model_logistic <- glm(model_formula, data=train, family="binomial")

log_odds_hat <- predict(model_logistic, newdata=train)
p_hat <- 1/(1 + exp(-log_odds_hat))

train_augmented <- model_logistic %>% 
  broom::augment() %>% 
  as_tibble() %>% 
  mutate(p_hat = 1/(1+exp(-.fitted)))

pred <- prediction(predictions = train_augmented$p_hat, labels = train_augmented$train.SeriousDlqin2yrs)
perf <- performance(pred, "tpr","fpr")

auc <- as.numeric(performance(pred,"auc")@y.values)
auc
```



# ROC curve

Based on the ultimate classifier you choose, plot a corresponding ROC curve.

```{r}
plot(perf, main=paste("Area Under the Curve =", round(auc, 3)))
abline(c(0, 1), lty=2)
```



# ROC curve for random guessing

Instead of using any predictor information as you did above, switch your
predictions to random guesses and plot the resulting ROC curve.

```{r}


pred_2 <- pred_2 <- prediction(predictions = rnorm(150000, .5, .15), labels = train$SeriousDlqin2yrs)
perf_2 <- performance(pred_2, "tpr","fpr")

auc <- as.numeric(performance(pred_2,"auc")@y.values)
auc

plot(perf_2, main=paste("Area Under the Curve =", round(auc, 3)))
abline(c(0, 1), lty=2)
```

```{r}
#generating predictions
model_logistic_2 <- glm(model_formula, data=test, family="binomial")
log_odds_hat_sub <- predict(model_logistic_2, newdata=test)
p_hat_sub <- 1/(1 + exp(-log_odds_hat_sub))
submission <- data.frame(p_hat_sub)
#submission['Id'] <- test$Id
```

